Concurrent Programming in Harmony

### 2021-07-30 book/paper.tex
Latest

Different transactions can have different coordinators.  In our
implementation, each bank and each coordinator is a thread.
\autoref{fig:2pc1} shows the code for a bank.
The state of a bank consists of the following local variables:
\begin{itemize}
\item \textit{self}: the bank's identifier;
\item \textit{balance}: the current balance in the account;
\item \textit{status}: either \texttt{.idle} or
$(\mathtt{.busy}, \mathit{coordinator}, \mathit{oldbalance})$,
where \textit{coordinator} is the identifier of the coordinator
of a transaction and \textit{oldbalance} is the balance
just before the transaction started;
\item \textit{received}: the set of messages received and handled so far.
\end{itemize}

>>>>

Different transactions can have different coordinators.  In our
implementation, each bank and each coordinator is a thread.
\autoref{fig:2pc1} shows the code for a bank.
The state of a bank consists of the following local variables:
\begin{itemize}
\item \textit{self}: the bank's identifier;
\item \textit{balance}: the current balance in the account;
\item \textit{status}: either contains () if the bank is not involved in an
ongoing transaction or contains the balance
just before the transaction started;
\item \textit{received}: the set of messages received and handled so far.
\end{itemize}
